---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pater

<!-- badges: start -->
<!-- badges: end -->

The goal of pater is to decompose a given pathname into meaningful tokens that will be later used to construct a regular expression useful when matching an HTTP request to a route handler.

Core to this are **path parameters** which are pieces of text you define in your route definitions and that will be filled when a new request comes in, they are useful because they act as identifiers for a given concept you care about.

Path parameters can appear *anywhere* you want inside a given path, they may share the same path segment or be next to plain text, given this the following are valid positions for path parameters:

- /text/:parameter
- /text/:parameter1-:parameter2
- /text1/:parameter1/text2{.:parameter2}
- /text1/*parameter

`pater` borrows its syntax from the original [path-to-regexp](https://github.com/pillarjs/path-to-regexp) implementation that you can read, understand and 
experiment with `pater` in R as the R implementation tries to be as close as
possible to the original.

## Installation

You can install the stable version of `pater` from CRAN with:

```{r}
install.packages("pater")
```

You can install the development version of `pater` like so:

``` r
# install.packages("pak")
pak::pak("JulioCollazos64/pater")
```
